Extended Data

### 2021-10-15 doc/manuscript/Dow_manuscript_Nature.Rmd
word count

##figures
EDF_map = "Extended Data Figure 1" 
EDF_growth_curves_all = "Extended Data Figure 2"  
EDF_climwin = "Extended Data Figure 3"
EDF_pheno_all = "Extended Data Figures 4-6"
EDF_pheno_Tmax_climwin = "Extended Data Figure 4"
EDF_pheno_Tmax_AprilMay = "Extended Data Figure 5"
EDF_tree_rings_TMAX_extended = "Extended Data Figure 6"
EDF_tree_rings_TMIN = "Extended Data Figure 7"

@@

*NOTE: In general, this needs to be condensed. The typical length of an article with 3-4 modest display items (figures and tables) is 2000-2500 words (summary paragraph plus body text). We're currently at ~2922 words (1613 intro + results, discussion 1319--too long!) and 1 modest + 2 large display items. Articles typically have 30-50 references (currently ok there)*

@@

<!--1309 words before Krista's edits. Goal: 700-800-->

>>>>

##figures
EDF_map = "Extended Data Figure 1" 
EDF_growth_curves_all = "Extended Data Figure 2"  
EDF_climwin = "Extended Data Figure 3"
EDF_pheno_all = "Extended Data Figures 4-5"
EDF_pheno_Tmax_climwin = "Extended Data Figure 4"
EDF_pheno_Tmax_AprilMay = "Extended Data Figure 5"
EDF_tree_rings_TMAX_extended = "Extended Data Figure 6"
EDF_tree_rings_TMIN = "Extended Data Figure 7"

@@

*NOTE: In general, this needs to be condensed. The typical length of an article with 3-4 modest display items (figures and tables) is 2000-2500 words (summary paragraph plus body text). We're currently at ~2562 words (1609 intro + results, discussion 953) and 1 modest + 2 large display items. Articles typically have 30-50 references (currently ok there)*

@@

<!--Currently 953. Goal: 700-800-->
